A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2021-07-28 Analysis/models.Rmd
update spr models, integrate into manuscript

```
## Summaries of LMER 
These have some heirarchical effects
```{r}
read_rds(here("Analysis/models/grnn_spr_lmer.rds")) %>% summary()
read_rds(here("Analysis/models/5-gram_spr_lmer.rds")) %>% summary()
read_rds(here("Analysis/models/txl_spr_lmer.rds")) %>% summary()
read_rds(here("Analysis/models/gpt_spr_lmer.rds")) %>% summary()

```{r diagnose-unhappiness, eval=F}

sad <- read_rds(here("Analysis/models/txl_spr.rds"))

summary(sad)

```
```{r summary-spr}

show_summary_spr <- function(model){
  intervals <- gather_draws(model, `b_.*`, regex=T) %>% mean_qi()

@@

```{r process-spr-models, eval=F}
ngram_spr <- read_rds(here("Analysis/models/5-gram_spr.rds")) %>% show_summary_spr() %>% mutate(model="5-gram")
txl_spr <- read_rds(here("Analysis/models/txl_spr.rds")) %>% show_summary_spr() %>% mutate(model="TXL")
grnn_spr <- read_rds(here("Analysis/models/grnn_spr.rds")) %>% show_summary_spr() %>% mutate(model="GRNN")
gpt_spr <- read_rds(here("Analysis/models/gpt_spr.rds")) %>% show_summary_spr() %>% mutate(model="GPT-2")

summ_spr <- ngram_spr %>% union(txl_spr) %>% union(grnn_spr) %>% union(gpt_spr) %>% write_rds(here("Analysis/models/brms_spr_summ.rds"))

>>>>

```
## Summaries of LMER 
These have some heirarchical effects

```{r summary-spr}

show_summary_spr <- function(model){

  stats <- summary(model)[["coefficients"]] %>% 
    as_tibble(rownames="Term") %>% 
    mutate(width=1.97*`Std. Error`,
           lower=round(Estimate-width,1),
           upper=round(Estimate+width,1),
           E=round(Estimate, digits=1),
           `Estimate`=str_c(E," [",lower,", ", upper,"]")
           ) %>% 
    select(Term, Estimate)

@@

```{r process-spr-models, eval=F}
ngram_spr <- read_rds(here("Analysis/models/5-gram_spr_lmer.rds")) %>% show_summary_spr() %>% mutate(model="5-gram")
txl_spr <- read_rds(here("Analysis/models/txl_spr_lmer.rds")) %>% show_summary_spr() %>% mutate(model="TXL")
grnn_spr <- read_rds(here("Analysis/models/grnn_spr_lmer.rds")) %>% show_summary_spr() %>% mutate(model="GRNN")
gpt_spr <- read_rds(here("Analysis/models/gpt_spr_lmer.rds")) %>% show_summary_spr() %>% mutate(model="GPT-2")

summ_spr <- ngram_spr %>% union(txl_spr) %>% union(grnn_spr) %>% union(gpt_spr) %>% write_rds(here("Analysis/models/lmer_spr_summ.rds"))

### 2021-07-28 Papers/Paper/manuscript.Rmd
update spr models, integrate into manuscript

In addition to the texts, @futrellNaturalStoriesCorpus2020 released reading time data from a SPR study they ran. They recruited 181 participants, most of whom read 5 of the stories. After reading each story, each participant answered 6 binary-choice comprehension questions. As a comparison to our A-maze models, we run similar models on the SPR corpus on Natural Stories [@futrellNaturalStoriesCorpus2020]. For comparability, we analyse only the first story each participant read, and, in line with @futrellNaturalStoriesCorpus2020, exclude participants who got less than 5/6 of the comprehension questions correct. To account for spill over effects known to exist in SPR, we analyse predictors at the current word as well as the past 3 words for all models. 
For linear models, we centered all predictors. We were unable to fit the full mixed effects model, so we used the best model that reasonably converged which had a by-subject random intercept and a per-word-token random intercept. We used regularizing priors(normal(350,50) for intercept, normal(0,5) for beta, exponential(.01) for sd and sigma). Models were run in brm [@burknerAdvancedBayesianMultilevel2018].

@@

summ_spr <- read_rds(here("Analysis/models/brms_spr_summ.rds")) %>% 
  pivot_wider(names_from="model", values_from=c(`Estimate`)) %>% 
  mutate(Term=factor(Term, 
                        levels=c("Intercept", 
                                 "surp_center",
                                 "length_center",
                                 "freq_center",
                                 "surp_center:length_center",
                                 "length_center:freq_center",
                                 "past_surp_center",
                                 "past_length_center",
                                 "past_freq_center",
                                 "past_surp_center:past_length_center",
                                 "past_length_center:past_freq_center",
                                 "past2_surp_center",
                                 "past2_length_center",
                                 "past2_freq_center",
                                 "past2_surp_center:past2_length_center",
                                 "past2_length_center:past2_freq_center",
                                 "past3_surp_center",
                                 "past3_length_center",
                                 "past3_freq_center",
                                 "past3_surp_center:past3_length_center",
                                 "past3_length_center:past3_freq_center"
                                 )
                                 )) %>% 
  arrange(Term) %>% 
  mutate(Term=c("Intercept", "Surprisal", "Length", "Frequency","Surp x Length", "Freq x Length",
                "Past Surprisal", "Past Length", "Past Freq", "Past Surp x Length", "Past Freq x Length",
                "2Past Surprisal", "2Past Length", "2Past Freq", "2Past Surp x Length", "2Past Freq x Length",
                "3Past Surprisal", "3Past Length", "3Past Freq", "3Past Surp x Length", "3Past Freq x Length"))

knitr::kable(summ_spr, format="latex", position="ht",caption="Predictions from fitted Bayesian regression models for SPR data. All terms were centered, but not rescaled. Units are in ms. Surprisal is per bit, length per character, and frequency per $log_2$ occurance per billion words.")

>>>>

In addition to the texts, @futrellNaturalStoriesCorpus2020 released reading time data from a SPR study they ran. They recruited 181 participants, most of whom read 5 of the stories. After reading each story, each participant answered 6 binary-choice comprehension questions. As a comparison to our A-maze models, we run similar models on the SPR corpus on Natural Stories [@futrellNaturalStoriesCorpus2020]. For comparability, we analyse only the first story each participant read, and, in line with @futrellNaturalStoriesCorpus2020, exclude participants who got less than 5/6 of the comprehension questions correct. To account for spill over effects known to exist in SPR, we analyse predictors at the current word as well as the past 3 words for all models. 
For linear models, we centered all predictors. We were unable to fit the full mixed effects model. The best model we could fit had by-subject random intercept, uncorrelated by-subject random slopes for surprisal, length and frequency, and  a per-word-token random intercept, fit with lme4, as this structure did not fit reliably in brms.

@@

summ_spr <- read_rds(here("Analysis/models/lmer_spr_summ.rds")) %>% 
  pivot_wider(names_from="model", values_from=c(`Estimate`)) %>% 
  mutate(Term=factor(Term, 
                        levels=c("(Intercept)", 
                                 "surp_center",
                                 "length_center",
                                 "freq_center",
                                 "surp_center:length_center",
                                 "length_center:freq_center",
                                 "past_surp_center",
                                 "past_length_center",
                                 "past_freq_center",
                                 "past_surp_center:past_length_center",
                                 "past_length_center:past_freq_center",
                                 "past2_surp_center",
                                 "past2_length_center",
                                 "past2_freq_center",
                                 "past2_surp_center:past2_length_center",
                                 "past2_length_center:past2_freq_center",
                                 "past3_surp_center",
                                 "past3_length_center",
                                 "past3_freq_center",
                                 "past3_surp_center:past3_length_center",
                                 "past3_length_center:past3_freq_center"
                                 )
                                 )) %>% 
  arrange(Term) %>% 
  mutate(Term=c("Intercept", "Surprisal", "Length", "Frequency","Surp x Length", "Freq x Length",
                "Past Surprisal", "Past Length", "Past Freq", "Past Surp x Length", "Past Freq x Length",
                "2Past Surprisal", "2Past Length", "2Past Freq", "2Past Surp x Length", "2Past Freq x Length",
                "3Past Surprisal", "3Past Length", "3Past Freq", "3Past Surp x Length", "3Past Freq x Length"))

knitr::kable(summ_spr, format="latex", position="ht",caption="Predictions from fitted regression models for SPR data. All terms were centered, but not rescaled. Units are in ms. Surprisal is per bit, length per character, and frequency per $log_2$ occurance per billion words. Uncertainty interval is +/- 1.97 standard error.")
